% Please use the skeleton file you have received in the
% invitation-to-submit email, where your data are already
% filled in. Otherwise please make sure you insert your
% data according to the instructions in PoSauthmanual.pdf
\documentclass{PoS}

\title{Summary of Working Group 4 : mixing and mixing-related $CP$ violation in the $B$ system}

\ShortTitle{All SM everything}

\author{\speaker{Alessandro Gaz}\\
        Nagoya\\
        E-mail: \email{gaz@hepl.phys.nagoya-u.ac.jp}\\
        \speaker{Vladimir V. Gligorov}\thanks{I would like to thank my mum, dad, and trade union representative for their support. Couldn't have done it without you!}\\
        LPNHE, Universit\'{e} Pierre et Marie Curie, Universit\'{e} Paris Diderot, CNRS/IN2P3, Paris, France\\
        E-mail: \email{vgligoro@lpnhe.in2p3.fr}\\
        \speaker{Dean Robinson}\\
        Cincinnati\\
        E-mail: \email{dean.robinson@uc.edu}\\
        }

%\author{Another Author\\
%        Affiliation\\
%        E-mail: \email{...}}

\abstract{$B$ mesons mix and in mixing do wonderful and amazing things.}

\FullConference{9th International Workshop on the CKM Unitarity Triangle\\
		28  November - 3 December 2016\\
		Tata Institute for Fundamental Research (TIFR), Mumbai, India}


\begin{document}

\input{introduction}

%\input{phis}
%\input{deltag}
%\input{deltam}
% ale: I think it makes more sense to have phi_s and deltaGamma_s in one section:
% vava : agree on all counts
\input{phis-deltags}
% and one section for Deltam_d,s and DeltaGamma_d:
\input{deltam-deltagd}
% (this reflects better the structure of the talks IMHO)
\input{alpha}
\input{beta}
\input{gamma}
\input{conclusion}

%\bibliographystyle{PoS}
\bibliography{skeleton}


\begin{thebibliography}{99}

% I'm not citing this, but I put it here just in case
%\bibitem{atlas_phis_7TeV}
%  G.~Aad \emph{et al.} (ATLAS Collaboration),
%  \emph{Flavor tagged time-dependent angular analysis of the $B^0_s \to J/\psi \phi$ decay
%    and extraction of $\Delta\Gamma_s$ and the weak phase $\phi_s$ in ATLAS},
%  \emph{Phys.~Rev.~D} {\bf 90}, 052007 (2014) [{\tt arXiv:1407.1796 hep-ex}].

\bibitem{atlas_phis_8TeV}
  G.~Aad \emph{et al.} (ATLAS Collaboration),
  \emph{Measurement of the CP-violating phase $\phi_s$ and the $B^0_s$ meson decay width
    difference with $B^0_s \to J/\psi \phi$ decays in ATLAS},
  \emph{JHEP} {\bf 1608}, 147 (2016) [{\tt arXiv:1601.03297 hep-ex}].

\bibitem{cms_phis}
  V.~Khachatryan \emph{et al.} (CMS Collaboration),
  \emph{Measurement of the CP-violating weak phase $\phi_s$ and the decay width difference
    $\Delta\Gamma_s$ using the $B^0_s \to J/\psi \phi(1020)$ decay channel in pp collisions
    at $\sqrt{s}$ = 8 TeV},
  \emph{Phys.~Lett.~B} {\bf 757}, 97 (2016) [{\tt arXiv:1507.07527 hep-ex}].

\bibitem{babar_cpt}
  J.~P.~Lees \emph{et al.} (BaBar Collaboration),
  \emph{Tests of CPT symmetry in $B^0-\overline{B}^0$ mixing and in $B^0 \to c\overline{c}K^0$ decays},
  \emph{Phys.~Rev.~D} {\bf 94}, 011101 (2016) [{\tt arXiv:1605.04545 hep-ex}].

\bibitem{babar_belle_D0h0}
  A.~Abdesselam \emph{et al.} (BaBar and Belle Collaborations),
  \emph{First Observation of CP Violation in $\overline{B}^0 \to
      D^{(*)}_{\rm CP} h^0$ Decays by a Combined Time-Dependent Analysis of BABAR and Belle Data}
  \emph{Phys.~Rev.~Lett.} {\bf 115}, 121604 (2015) [{\tt arXiv:1505.04147 hep-ex}].
  
\bibitem{belle_rhorho}
  P.~Vanhoefer  \emph{et al.} (Belle Collaboration),
  \emph{Study of $\mathbf{B^{0}\rightarrow\rho^{+}\rho^{-}}$
    decays and implications for the CKM angle $\mathbf{\phi_2}$},
  \emph{Phys.~Rev.~D} {\bf 93}, 032010 (2016) [{\tt arXiv:1510.01245 hep-ex}].
  
\end{thebibliography}
  
\end{document}
